Structured Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2016-10-19 R0V0.tex
Finish proof of THeorem 2

In case of full decentralization with $n_i=m_i=1$, for every index $i\in\mathbb{N}_{[1,N]}$,  the set $\Xi$ is defined with $\mathbf{C}_j=\{e_j\}$, $\mathscr{K}(i)=\{i\}$ and $\mathbf{X}_i=\{x_i\}$.

@@

	Note that, due to the structure of the matrix $K$, for each component $i\in\mathbb{N}_{[1,N]}$ of the feedback law $k^\ast$ defined by  Equation~\eqref{eq:contracting feedback law} is given by
	\begin{equation*}
		k_i^\ast(t,s)=u_i^\ast(t)+\int_0^sK_i(\widetilde{\gamma}_i(\sigma),k_i^\ast(t,s))\widetilde{\gamma}_i'(\sigma)\,d\sigma\;,
	\end{equation*}
	where $\widetilde{\gamma}_i(\cdot)\in\mathbf{X}(\mathscr{K}(i))$.

	Problem~\ref{problem formulation}. This concludes the proof of Theorem \ref{thm:main result}.
\end{proof}

>>>>

In case of full decentralization with $n_i=m_i=1$, for every index $i\in\mathbb{N}_{[1,N]}$,  the set $\Xi$ is defined with $\mathbf{C}_j=\{e_j\}$, $\mathscr{K}(i)=\{i\}$ and $\mathbf{X}(\mathscr{K}(i))=\{x_i\}$.

@@

	Note that, due to the constraint $Y\in\Xi$ and the fact that $W$ is diagonal, each component $i\in\mathbb{N}_{[1,N]}$ of the feedback law $k^\ast$, defined by  Equation~\eqref{eq:contracting feedback law}, is given by
	\begin{equation*}
		k_i^\ast(t,s)=u_i^\ast(t)+\int_0^sK_i(\widetilde{\gamma}_i(\sigma),k_i^\ast(t,s))\widetilde{\gamma}_i'(\sigma)\,d\sigma\;,
	\end{equation*}
	where $\widetilde{\gamma}_i(\cdot)\in\mathbf{X}(\mathscr{K}(i))$.
	Thus, $k^\ast$ satisfies the constraint imposed in Problem~\ref{problem formulation}. This concludes the proof of Theorem \ref{thm:main result}.
\end{proof}
